Higher Levels of Education in the U.S. May Positively Correlate to Greater Levels of Financial Satisfaction and Social Worth

### 2023-03-16 outputs/paper/paper.qmd
update supplementary survey

knitr::include_graphics("./supplementary_survey/suppl_surv_01.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_2.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_3.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_4.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_5.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_6.png")

>>>>

knitr::include_graphics("./supplementary_survey/suppl_surv_01.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_02.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_03.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_04.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_05.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_06.png")
